%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research Projects}
\label{sec:proj}
\vspace{-5mm}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
\begin{multicols}{2}
%---------------------------------------------------------
  \cvprojentry
    {Supported by ETH Grant ETH-12 16-2} % Job title
    {Sun2Ice: Monitoring calving glaciers from solar-powered UAVs} % Organization
    {Z\"{u}rich, Switzerland} % Location
    {2017 - Present} % Date(s)
    {Demonstrated the \emph{first-ever} autonomous, solar-powered flights of a UAV in a polar region, including a flight of more than 12 hours duration, and the survey of the calving front of Bowdoin Glacier, \emphdescriptionstyle{Northwest Greenland}, which revealed the opening of a crack leading to a major calving event the following week.} % Milestone(s) of project
    {Lead UAV operations in Qaanaaq, Greenland during glacier monitoring field campaign.} % Description(s) of tasks/responsibilities
	{http://sun2ice.ethz.ch}
%---------------------------------------------------------
  \cvprojentry
    {Supported by Armasuisse Science \& Technology (Contract \#043-12)} % Job title
    {SolAIR: \textbf{S}olar-powered \textbf{A}utomated \textbf{A}erial \textbf{I}maging and \textbf{R}econnaissance using \textbf{I}nfrared \textbf{C}ameras} % Organization
    {Z\"{u}rich, Switzerland} % Location
    {2016} % Date(s)
    {Demonstrated a fully autonomous, 26 hour, solar-powered flight with the AtlantikSolar UAV while live-streaming onboard infrared camera feed and tracking thermal updrafts.} % Milestone(s) of project
    {Developed and deployed autonomous take-off and landing algorithms/logic for the AtlantikSolar UAV.} % Description(s) of tasks/responsibilities
	{}
	
%---------------------------------------------------------
  \cvprojentry
    {Supported by Swissnex Brazil, Swissando, and ETH Global} % Job title
    {Adventura AtlantikSolar@Brazil} % Organization
    {Bel\`{e}m, Brazil} % Location
    {2015} % Date(s)
    {Performed the \emph{first-ever} autonomous solar-powered flight over the \emphdescriptionstyle{Amazon rain forest}. Supported Brazilian partners at SIPAM (Brazilian Amazon Protection System, part of the Brazilian Ministry of Defense) in the aerial monitoring and mapping of a disaster site on the Rio Pará - a sunken ship involving 4400 dead cattle and 750 tons of spilled oil.} % Milestone(s) of project
    {Co-organized field campaign, supported field demonstrations, gave public workshops and talks.} % Description(s) of tasks/responsibilities
	{http://www.swissnexbrazil.org/atlantiksolar/}
	
%---------------------------------------------------------
  \cvprojentry
    {Supported by private investors and internal laboratory budget} % Job title
    {AtlantikSolar: A UAV for the first-ever autonomous solar-powered crossing of the Atlantic Ocean} % Organization
    {Z\"{u}rich, Switzerland} % Location
    {2014 - 2017} % Date(s)
    {Current world solar-powered endurance record for aircraft below \unit{50}{kg} after \unit{81.5}{hr} flight demonstration in Summer 2015.} % Milestone(s) of project
    {System identification \& modeling, flight control, guidance, \& planning for robust autonmous flight behavior in high winds and uncertain environments. Investigation and testing of local perception techniques and sensors for near terrain flight. Autopilot and onboard computation framework development.} % Description(s) of tasks/responsibilities
	{http://www.atlantiksolar.ethz.ch/}
	
%---------------------------------------------------------
  \cvprojentry
    {Supported by the European Commission under the 7th European Framework Programme (\#600958)} % Job title
    {SHERPA: \textbf{S}mart collaboration between \textbf{H}umans and ground-a\textbf{E}rial \textbf{R}obots for im\textbf{P}roving rescuing activities in \textbf{A}lpine environments} % Organization
    {Z\"{u}rich, Switzerland} % Location
    {2014 - 2017} % Date(s)
    {Field demonstration of an autonomous multi-UAV, collaborative aerial mapping and 3-D reconstruction mission with the senseSoar solar-powered UAV and an R-MAX helicopter.} % Milestone(s) of project
    {Platform specific integration within SHERPA Delegation Framework: C++/ROS based programming for task
allocation among the multi-actor SHERPA team. Aircraft integration, flight-testing, and autonomy development for senseSoar solar-powered UAV.} % Description(s) of tasks/responsibilities
	{http://www.sherpa-project.eu/}

%---------------------------------------------------------
  \cvprojentry
    {Supported by the European Commission under the 7th European Framework Programme (\#285417)} % Job title
    {ICARUS: Robotic Search and Rescue} % Organization
    {Z\"{u}rich, Switzerland} % Location
    {2014 - 2016} % Date(s)
    {Field demonstration of robotic search and rescue missions including real-time victim detection from fixed-wing aircraft with live-streaming GPS localization.} % Milestone(s) of project
    {Designed and demonstrated a LiDAR-based auto-landing controller for fixed-wing platforms. Supported final field-trails in Marche-en-Famenne, BE.} % Description(s) of tasks/responsibilities
    {http://www.fp7-icarus.eu/}
    
%---------------------------------------------------------
  \cvprojentry
    {Supported by the Paul G. Allen Family Foundation} % Job title
    {Multi-Agent Airborne Laboratory for Cryospheric Remote Sensing} % Organization
    {Lawrence, KS, USA} % Location
    {2014} % Date(s)
    {Development and testing of distributed sensors in coordinated flight in order to better measure and characterize the impact of climate changes on fast-flowing glaciers.} % Milestone(s) of project
    {Aided writing of full proposal. Applied integrated guidance, control, and trajectory generation to the case of UAS formation concepts supporting aerial ice penetrating synthetic aperture radar systems in a relative formation holding approach.} % Description(s) of tasks/responsibilities
    {}
    
%---------------------------------------------------------
  \cvprojentry
    {Supported by the National Science Foundation (NSF) under grant ANT-0424589} % Job title
    {CReSIS: Center for Remote Sensing of Ice Sheets} % Organization
    {Lawrence, KS, USA} % Location
    {2012 - 2014} % Date(s)
    {Conducted the first successful bedrock mapping of Antarctic ice sheets via radar sounding from an autonomous UAS.} % Milestone(s) of project
    {Designed and manufactured various components for radar integration and Arctic outfitting of the University of Kansas Aerospace Department's G1X UAS. Participated in \emphdescriptionstyle{8-week deployment} as mission planner and ground station operator for autonomous operations of a radar-integrated UAS platform in \emphdescriptionstyle{Western Antarctica}.} % Description(s) of tasks/responsibilities
    {https://www.cresis.ku.edu/}

%---------------------------------------------------------
\end{multicols}
\end{cventries}
