%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}
\label{sec:proj}
%\vspace{-5mm}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%\begin{multicols}{2}

%---------------------------------------------------------
  \cvprojwideentry
  	{Drop \& Recovery Drones} % Project
  	{Automated Remote Sensor Management via Unmanned Aerial Systems} % Project subtext
    {Supported by Armasuisse Science \& Technology (Proj. no. 050-45, contract no. 20190201)} % Support
    {2019} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Co-authored project proposal.}
        \item {Supervised/managed student/engineering work on platform and payload development and aided field campaign on Gorner Glacier, Switzerland.}
        \item {Fully automatic BVLOS dropping of long-term GNSS monitoring stations on Gorner Glacier, Switzerland.}
      \end{cvitems}
    } % Description
    {https://youtu.be/1tvYj1aGEUc} % website
    {\showprojectdescriptions}

%---------------------------------------------------------
  \cvprojwideentry
  	{Predicting the Weather} % Project
  	{On-board Forecasting of Local 3D Wind Fields for Autonomous and
Environment-aware Operation of Unmanned Aerial Vehicles} % Project subtext
    {Supported by Intel Network on Intelligent Systems (Proj. 3-26-15)} % Support
    {\parbox{\linewidth}{2018\linebreak}} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Co-authored project proposal.}
      \end{cvitems}
    } % Description
    {} % website
    {\showprojectdescriptions}

\vspace{-9pt}

%---------------------------------------------------------
  \cvprojwideentry
  	{Sun2Ice} % Project
  	{Monitoring calving glaciers from solar-powered UAVs} % Project subtext
    {Supported by ETH Grant ETH-12 16-2} % Support
    {2017 - 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Co-authored project proposal.}
        \item {Organized / lead UAV operations in Qaanaaq, Greenland during glacier monitoring field campaign.}
        \item {\emph{First-ever} autonomous, solar-powered flights of a UAV in a polar region, including a flight of more than 12 hours duration, and the survey of the calving front of Bowdoin Glacier, \emphdescriptionstyle{Northwest Greenland}, which revealed the opening of a crack leading to a major calving event the following week.}
      \end{cvitems}
    } % Description
    {http://sun2ice.ethz.ch} % website
    {\showprojectdescriptions}
    
%%---------------------------------------------------------
\cvprojwideentry
  	{SolAIR} % Project
  	{Solar-powered Automated Aerial Imaging and Reconnaissance using Infrared Cameras} % Project subtext
    {Supported by Armasuisse Science \& Technology (Contract \#043-12)} % Support
    {2016} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Developed and deployed autonomous take-off and landing algorithms/logic for the AtlantikSolar UAV.}
        \item {Demonstrated a fully autonomous, 26 hour, solar-powered flight with the AtlantikSolar UAV while live-streaming onboard infrared camera feed and tracking thermal updrafts.}
      \end{cvitems}
    } % Description
    {https://youtu.be/8m76Mx9m2nM} % website
    {\showprojectdescriptions}
    
%%---------------------------------------------------------
\cvprojwideentry
  	{Adventura AtlantikSolar@Brazil} % Project
  	{} % Project subtext
    {Supported by Swissnex Brazil, Swissando, and ETH Global} % Support
    {2015} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Co-organized field campaign, supported field demonstrations, gave public workshops and talks.}
        \item {Performed the \emph{first-ever} autonomous solar-powered flight over the \emphdescriptionstyle{Amazon rain forest}, supporting Brazilian partners at SIPAM (Brazilian Amazon Protection System, part of the Brazilian Ministry of Defense) in the aerial monitoring and mapping of a disaster site on the Rio Pará - a sunken ship involving 4400 dead cattle and 750 tons of spilled oil.}
      \end{cvitems}
    } % Description
    {http://www.swissnexbrazil.org/atlantiksolar/} % website
    {\showprojectdescriptions}

%%---------------------------------------------------------
\cvprojwideentry
  	{AtlantikSolar} % Project
  	{A UAV for the first-ever autonomous solar-powered crossing of the Atlantic Ocean} % Project subtext
    {Supported by private investors and internal laboratory budget} % Support
    {2014 - 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {System identification \& modeling, flight control, guidance, \& planning for robust autonmous flight behavior in high winds and uncertain environments.}
        \item {Autopilot and onboard software framework development.}
        \item {Current world solar-powered endurance record for aircraft below \unit{50}{kg} after \unit{81.5}{hr} flight demonstration in Summer 2015.}
      \end{cvitems}
    } % Description
    {http://www.atlantiksolar.ethz.ch/} % website
    {\showprojectdescriptions}

%%---------------------------------------------------------
\cvprojwideentry
  	{SHERPA} % Project
  	{\textbf{S}mart collaboration between \textbf{H}umans and ground-a\textbf{E}rial \textbf{R}obots for im\textbf{P}roving rescuing activities in \textbf{A}lpine environments} % Project subtext
    {Supported by the European Commission under the 7th European Framework Programme (\#600958)} % Support
    {\parbox{\linewidth}{\raggedright 2014 - 2017\linebreak}} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Platform specific integration within SHERPA Delegation Framework: C++/ROS based programming for task allocation among the multi-actor SHERPA team.}
        \item {Aircraft integration, flight-testing, and autonomy development for senseSoar solar-powered UAV.}
        \item {Field demonstration of an autonomous multi-UAV, collaborative aerial mapping and 3-D reconstruction mission with the senseSoar solar-powered UAV and an R-MAX helicopter.}
      \end{cvitems}
    } % Description
    {http://www.sherpa-project.eu/} % website
    {\showprojectdescriptions}

%%---------------------------------------------------------
\cvprojwideentry
  	{ICARUS} % Project
  	{Robotic Search and Rescue} % Project subtext
    {Supported by the European Commission under the 7th European Framework Programme (\#285417)} % Support
    {2014 - 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Designed and demonstrated a LiDAR-based auto-landing controller for fixed-wing platforms.}
        \item {Field demonstration of robotic search and rescue missions including real-time victim detection from fixed-wing aircraft with live-streaming GPS localization.}
      \end{cvitems}
    } % Description
    {http://www.fp7-icarus.eu/} % website
    {\showprojectdescriptions}

%%---------------------------------------------------------
\cvprojwideentry
  	{Multi-Agent Airborne Laboratory for Cryospheric Remote Sensing} % Project
  	{} % Project subtext
    {Supported by the Paul G. Allen Family Foundation} % Support
    {2014} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Aided writing of full proposal.}
        \item {Applied integrated guidance, control, and trajectory generation to the case of UAS formation concepts supporting aerial ice penetrating synthetic aperture radar systems in a relative formation holding approach.}
      \end{cvitems}
    } % Description
    {} % website
    {\showprojectdescriptions}
    
%%---------------------------------------------------------
\cvprojwideentry
  	{CReSIS} % Project
  	{Center for Remote Sensing of Ice Sheets} % Project subtext
    {Supported by the National Science Foundation (NSF) under grant ANT-0424589} % Support
    {2012 - 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Designed and manufactured various components for radar integration and Arctic outfitting of the University of Kansas Aerospace Department's G1X UAS.}
        \item {Participated in \emphdescriptionstyle{8-week deployment} as mission planner and ground station operator for autonomous operations of a radar-integrated UAS platform in \emphdescriptionstyle{Western Antarctica}.}
        \item {Conducted the first successful bedrock mapping of Antarctic ice sheets via radar sounding from an autonomous UAV, BVLOS.}
      \end{cvitems}
    } % Description
    {https://www.cresis.ku.edu/} % website
    {\showprojectdescriptions}
    
%---------------------------------------------------------
%\end{multicols}
\end{cventries}
