%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}

\headersocialstyle{
\ifthenelse{\isundefined{\@gscholar}}%
  {}%
  {%
    \href{https://scholar.google.ch/citations?user=R5Fs1A4AAAAJ\&hl=en}{\faGraduationCap\acvHeaderIconSep https://scholar.google.ch/citations?user=R5Fs1A4AAAAJ\&hl=en}%
  }%
}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%-------------------------------------------------------------------------------
%	Journal Papers
%-------------------------------------------------------------------------------

\begin{flushleft}
\entrytitlestyle{Journal Papers}
\end{flushleft}

\cvpubentry
	{Journal of Field Robotics (JFR)} % publisher
	{Long-duration Fully Autonomous Operation of Rotorcraft Unmanned Aerial Systems for Remote-sensing Data Acquisition} % title
	{D. Malyuta, C. Brommer, D. Hentzen, \textbf{T. Stastny}, R. Siegwart, and R. Brockers} % author(s)
	{Vol. 37(1). pp. 137--157} % publisher details
	{2020} % date
	{} % link
	{} % extra info

\cvpubentry
	{IEEE Robotics and Automation Letters} % publisher
	{Attitude and Cruise Control of a VTOL Tiltwing UAV} % title
	{D. Rohr, \textbf{T. Stastny}, S. Verling, and R. Siegwart} % author(s)
	{Vol. 4(3). pp. 2683--2690} % publisher details
	{2019} % date
	{} % link
	{} % extra info

\cvpubentry
	{IEEE Robotics and Automation Letters} % publisher
	{Free LSD: Prior-free Visual Landing Site Detection for Autonomous Planes} % title
	{T. Hinzmann, \textbf{T. Stastny}, C. Cadena, R. Siegwart, and I. Gilitschenski} % author(s)
	{Vol. 3(3). pp. 2545--2552} % publisher details
	{2018} % date
	{} % link
	{} % extra info
	
\cvpubentry
	{Journal of Field Robotics (JFR)} % publisher
	{Robotic Technologies for Solar-powered UAVs: Fully Autonomous Updraft-aware Aerial Sensing for Multiday Search-and-rescue Missions} % title
	{P. Oettershagen, \textbf{T. Stastny}, T. Hinzmann, K. Rudin, T. Mantel, A. Melzer, B. Wawrzacz, G. Hitz, and R. Siegwart} % author(s)
	{Vol. 35(4). pp. 612--640} % publisher details
	{2018} % date
	{} % link
	{} % extra info

\cvpubentry
	{Journal of Field Robotics (JFR)} % publisher
	{Design of Small Hand-launched Solar-powered UAVs: From Concept Study to a Multi-day World Endurance Record Flight} % title
	{P. Oettershagen, A. Melzer, Mantel, K. Rudin, \textbf{T. Stastny}, B. Wawrzacz, T. Hinzmann, S. Leutenegger, K. Alexis, and R. Siegwart} % author(s)
	{Vol. 34(7). pp. 1352--1377} % publisher details
	{2017} % date
	{} % link
	{} % extra info

\cvpubentry
	{Journal of Dynamic Systems, Measurement, and Control} % publisher
	{Collision and Obstacle Avoidance in Unmanned Aerial Systems Using Morphing Potential Field Navigation and Nonlinear Model Predictive Control} % title
	{\textbf{T. Stastny}, G. Garcia, S. Keshmiri} % author(s)
	{Vol. 137(1)} % publisher details
	{2015} % date
	{} % link
	{} % extra info
	
\cvpubentry
	{International Journal of Intelligent Unmanned Systems} % publisher
	{Nonlinear Model Predictive Controller Robustness Extension for Unmanned Aircraft} % title
	{G. Garcia, S. Keshmiri, \textbf{T. Stastny}} % author(s)
	{Vol. 3(2/3). pp. 93--121} % publisher details
	{2015} % date
	{} % link
	{} % extra info

\cvpubentry
	{IEEE Transactions on Control Systems Technology} % publisher
	{Robust and Adaptive Nonlinear Model Predictive Controller for Unsteady and Highly Nonlinear Unmanned Aircraft} % title
	{G. Garcia, S. Keshmiri, \textbf{T. Stastny}} % author(s)
	{Vol. 23(4). pp 1620--1627} % publisher details
	{2014} % date
	{} % link
	{} % extra info

%-------------------------------------------------------------------------------
%	Book Chapters
%-------------------------------------------------------------------------------
\clearpage
\begin{flushleft}
\entrytitlestyle{Book Chapters}
\end{flushleft}

\cvpubentry
	{Robot Operating System (ROS), The Complete Reference (Volume 2)} % publisher
	{Model Predictive Control for Trajectory Tracking of Unmanned Aerial Vehicles Using Robot Operating System} % title
	{M. Kamel, \textbf{T. Stastny}, K. Alexis, R. Siegwart} % author(s)
	{pp. 3--39} % publisher details
	{2017} % date
	{} % link
	{} % extra info

%-------------------------------------------------------------------------------
%	Peer Reviewed Conference Papers
%-------------------------------------------------------------------------------

\begin{flushleft}
\entrytitlestyle{Conference Papers}
\end{flushleft}

\cvpubentry
	{AIAA Guidance, Navigation, and Control (GNC) Conference} % publisher
	{Full Envelope System Identification of a VTOL Tailsitter UAV} % title
	{C. Olsson, S. Verling, \textbf{T. Stastny}, and R. Siegwart} % author(s)
	{} % publisher details
	{2021} % date
	{} % link
	{\textit{Accepted for publication}} % extra info

\cvpubentry
	{International Conference on Unmanned Aircraft Systems (ICUAS)} % publisher
	{Differential Sweep Attitude Control for Swept Wing UAVs} % title
	{M. Harms, N. Kaufmann, F. Rockenbauer, N. Lawrance, \textbf{T. Stastny}, and R. Siegwart} % author(s)
	{} % publisher details
	{2020} % date
	{} % link
	{} % extra info
	
\cvpubentry
	{IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS)} % publisher
	{On Flying Backwards: Preventing Run-away of Small, Low-speed, Fixed-wing UAVs in Strong Winds} % title
	{\textbf{T. Stastny} and R. Siegwart} % author(s)
	{} % publisher details
	{2019} % date
	{} % link
	{} % extra info

\cvpubentry
	{IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS)} % publisher
	{Disturbance Estimation and Rejection for High-Precision Multirotor Position Control} % title
	{D. Hentzen, \textbf{T. Stastny}, R. Siegwart, and R. Brockers} % author(s)
	{} % publisher details
	{2019} % date
	{} % link
	{} % extra info

\cvpubentry
	{American Control Conference (ACC)} % publisher
	{Locally Power-optimal Nonlinear Model Predictive Control for Fixed-wing Airborne Wind Energy} % title
	{\textbf{T. Stastny}, E. Ahbe, M. Dangel, and R. Siegwart} % author(s)
	{} % publisher details
	{2019} % date
	{} % link
	{} % extra info

\cvpubentry
	{IEEE International Conference on Robotics and Automation (ICRA)} % publisher
	{Fault-tolerant Flight Control of a VTOL Tailsitter UAV} % title
	{S. Fuhrer, S. Verling, \textbf{T. Stastny}, and R. Siegwart} % author(s)
	{} % publisher details
	{2019} % date
	{} % link
	{} % extra info

\cvpubentry
	{IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS)} % publisher
	{Towards Autonomous Stratospheric Flight: A Generic Global System Identification Framework for Fixed-Wing Platforms} % title
	{J. Lee, T. Muskardin, C. Pacz, P. Oettershagen, \textbf{T. Stastny}, I. Sa, R. Siegwart, and K. Kondak} % author(s)
	{} % publisher details
	{2018} % date
	{} % link
	{} % extra info

\cvpubentry
	{International Conference on Unmanned Aircraft Systems (ICUAS)} % publisher
	{Nonlinear Model Predictive Guidance for Fixed-wing UAVs Using Identified Control Augmented Dynamics} % title
	{\textbf{T. Stastny} and R. Siegwart} % author(s)
	{} % publisher details
	{2018} % date
	{} % link
	{} % extra info

\cvpubentry
	{American Control Conference (ACC)} % publisher
	{Gone with the Wind: Nonlinear Guidance for Small Fixed-wing Aircraft in Arbitrarily Strong Windfields} % title
	{L. Furieri, \textbf{T. Stastny}, L. Marconi, R. Siegwart, and I. Gilitschenski} % author(s)
	{} % publisher details
	{2017} % date
	{} % link
	{\textbf{Best Paper Award}} % extra info
	
\cvpubentry
	{IEEE International Conference on Robotics and Automation (ICRA)} % publisher
	{Model-based Transition Optimization for a VTOL Tailsitter} % title
	{S. Verling, \textbf{T. Stastny}, G. B{\"a}ttig, K. Alexis, and R. Siegwart} % author(s)
	{} % publisher details
	{2017} % date
	{} % link
	{} % extra info
	
\cvpubentry
	{IEEE International Conference on Robotics and Automation (ICRA)} % publisher
	{Model-based Wind Estimation for a Hovering VTOL Tailsitter UAV} % title
	{Y. Demitri, S. Verling, \textbf{T. Stastny}, A. Melzer, and R. Siegwart} % author(s)
	{} % publisher details
	{2017} % date
	{} % link
	{} % extra info
		
\cvpubentry
	{AIAA Guidance, Navigation, and Control (GNC) Conference} % publisher
	{Nonlinear MPC for Fixed-wing UAV Trajectory Tracking: Implementation and Flight Experiments} % title
	{\textbf{T. Stastny}, A. Dash, and R. Siegwart} % author(s)
	{} % publisher details
	{2017} % date
	{} % link
	{} % extra info

\cvpubentry
	{IEEE Aerospace Conference} % publisher
	{Perpetual Flight with a Small Solar-powered UAV: Flight Results, Performance Analysis and Model Validation} % title
	{P. Oettershagen, A. Melzer, T. Mantel, K. Rudin, \textbf{T. Stastny}, B. Wawrzacz, T. Hinzmann, K. Alexis, and R. Siegwart} % author(s)
	{} % publisher details
	{2016} % date
	{} % link
	{} % extra info


\cvpubentry
	{International Symposium on Experimental Robotics (ISER)} % publisher
	{Collaborative 3D Reconstruction Using Heterogeneous UAVs: System and Experiments} % title
	{T. Hinzmann, \textbf{T. Stastny}, G. Conte, P. Doherty, P. Rudol, M. Wzorek, I. Gilitschenski, E. Galceran, and R. Siegwart} % author(s)
	{} % publisher details
	{2016} % date
	{} % link
	{} % extra info

\cvpubentry
	{International Conference on Principles and Practice of Multi-Agent Systems} % publisher
	{A Collaborative Framework for 3D Mapping Using Unmanned Aerial Vehicles} % title
	{P. Doherty, J. Kvarnstr{\"o}m, P. Rudol, M. Wzorek, G. Conte, C. Berger, T. Hinzmann, \textbf{T. Stastny}} % author(s)
	{} % publisher details
	{2016} % date
	{} % link
	{} % extra info

\cvpubentry
	{Field and Service Robotics (FSR)} % publisher
	{Long-Endurance Sensing and Mapping using a Hand-Launchable Solar-Powered UAV} % title
	{Oettershagen, \textbf{T. Stastny}, T. Mantel, A. Melzer, K. Rudin, P. Gohl, G. Agamennoni, K. Alexis, and R. Siegwart} % author(s)
	{} % publisher details
	{2015} % date
	{} % link
	{} % extra info

\cvpubentry
	{International Symposium on Visual Computing (ISVC)} % publisher
	{Victim Detection from a Fixed-Wing UAV: Experimental Results} % title
	{A. Vempati, G. Agamennoni, \textbf{T. Stastny}, and R. Siegwart} % author(s)
	{} % publisher details
	{2015} % date
	{} % link
	{} % extra info
	
\cvpubentry
	{AIAA Guidance, Navigation, and Control (GNC) Conference} % publisher
	{Robust Three-Dimensional Collision Avoidance for Fixed-Wing Unmanned Aerial Systems} % title
	{\textbf{T. Stastny}, G. Garcia, S. Keshmiri} % author(s)
	{} % publisher details
	{2015} % date
	{} % link
	{} % extra info
	
\cvpubentry
	{AIAA Guidance, Navigation, and Control (GNC) Conference} % publisher
	{Nonlinear Parameter Estimation of Unmanned Aerial Vehicles in Wind Shear Using Artificial Neural Networks} % title
	{\textbf{T. Stastny}, R. Lykins, S. Keshmiri} % author(s)
	{} % publisher details
	{2013} % date
	{} % link
	{} % extra info
		
\cvpubentry
	{AIAA Infotech@ Aerospace} % publisher
	{Flight Testing and Evaluation of the Structural Response to Flight Loads of a Small Scale Unmanned Aerial System} % title
	{J. Sebes, W. Vanskike, M. Williams, S. McCandless, \textbf{T. Stastny}, G. Worden, N. Brunkhorst} % author(s)
	{} % publisher details
	{2012} % date
	{} % link
	{} % extra info

\cvpubentry
	{AIAA Modeling and Simulation Technologies Conference} % publisher
	{Hawkeye UAV Dynamic Analysis} % title
	{W. Vanskike, M. Williams, \textbf{T. Stastny}, A. Ghate, S. McCandless, T. Peckman} % author(s)
	{} % publisher details
	{2011} % date
	{} % link
	{} % extra info

%-------------------------------------------------------------------------------
%	Magazine Articles
%-------------------------------------------------------------------------------

\begin{flushleft}
\entrytitlestyle{Magazine Articles}
\end{flushleft}
	
\cvpubentry
	{Ruimtevaart} % publisher
	{Mars Exploration? Unleash the Swarms!} % title
	{\textbf{T. Stastny}} % author(s)
	{Vol. 2013(1), pp. 8--11. Netherlands Space Society (NVR)} % publisher details
	{2013} % date
	{} % link
	{} % extra info
	
%-------------------------------------------------------------------------------
%	Patents
%-------------------------------------------------------------------------------

\begin{flushleft}
\entrytitlestyle{Patents}
\end{flushleft}

\cvpubentry
	{US Patent 10,464,620} % publisher
	{Vehicles Configured For Navigating Surface Transitions} % title
	{M. Arigoni, R. Simpson, S. Fuhrer, P. Beardsley, D. Mammolo, M. Burri, M. Bischoff, \textbf{T. Stastny}, L. Rodgers, D. Krummenacher, and R. Siegwart} % author(s)
	{} % publisher details
	{2019} % date
	{} % link
	{} % extra info

%---------------------------------------------------------
\end{cventries}
