%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research Experience}
\label{sec:exp}
%\vspace{-5mm}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

%\descriptionstyle{	
%	Grants: Authorship of \textbf{successful} research proposals with funding totaling \textbf{$>$1.7M USD} \\
%	Field experience: Organization/participation of/in aerial-robotic field-campaigns to the Arctic, Antarctic, Amazon, and Swiss/Italian Alps
%	}

\begin{cventries}
%\begin{multicols}{2}

%---------------------------------------------------------
\cvexpentry
  	{Autonomous Systems Lab (ASL), ETH Z\"{u}rich} % Institute
  	{Senior Researcher} % Position
    {} % Subject
    {Since 10/2020} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
      	\item \textbf{Team lead} for research activities related to control of fixed-wing and hybrid, tilt-wing UAVs. Supervision of several PhD, Masters, and Bachelors students.
      \end{cvitems}
    } % Description
    {} % website
    {true}
    {}
    %\vspace{-12pt}

%---------------------------------------------------------
\cvexpentry
  	{Autonomous Systems Lab (ASL), ETH Z\"{u}rich} % Institute
  	{Research Assistant} % Position
    {} % Subject
    {2014 - 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
      	\item Research on control, modeling, system identification, state estimation, and planning for UAVs operating in extreme environments. Supervision of \textbf{50+} Masters and Bachelors theses. Core researcher on EU FP7 search-and-rescue robotics projects \emph{SHERPA} and \emph{ICARUS}, the \emph{AtlantikSolar} solar-powered UAV, the ESA precision-farming project \emph{SOLAR3}, and several Armasuisse S+T contracts.
		\item[] \hspace{-1.2em} \emph{Research / Project Milestones:}
		\item \textbf{Supervised/Managed} student/engineering work on platform and payload development towards a fully automatic BVLOS dropping of GNSS monitoring stations on the Gorner Glacier, Switzerland, from a multi-rotor UAV, within the Armasuisse S+T \emph{Drop \& Recovery Drones} project. \weblink{https://youtu.be/1tvYj1aGEUc}{https://youtu.be/1tvYj1aGEUc}
		\item Contributed to the \emph{first} networked (via Swisscom), BVLOS flight in Switzerland over Lake Neuchatel. \weblink{https://youtu.be/ks-TiJP3dxs}{https://youtu.be/ks-TiJP3dxs}
		\item \textbf{Organized/Lead} UAV operations in Qaanaaq, \textbf{Northwest Greenland} for the 2017 glacier monitoring field campaign of ETH Foundation project \emph{Sun2Ice}, resulting in \emph{first-ever} autonomous, BVLOS, solar-powered flights of a UAV in a polar region. website: \weblink{http://sun2ice.ethz.ch}{http://sun2ice.ethz.ch}, video: \weblink{https://youtu.be/wyS6W1t_ryQ}{https://youtu.be/wyS6W1t\_ryQ}
		\item \textbf{Co-Organized/Lead} field operations for Swissnex Brazil Project \emph{Adventura AtlantikSolar@Brazil}, resulting in \emph{first-ever} solar-powered flights of a UAV over the Amazon rainforest and the aerial monitoring/mapping of an oil spill on the Rio Par\'{a}. \weblink{http://www.swissnexbrazil.org/atlantiksolar/}{http://www.swissnexbrazil.org/atlantiksolar/}
		%\item Developed automatic take-off and landing strategies towards a fully autonomous, continuous 26-hour search-and-rescue flight within the Armasuisse S+T \emph{SOLAIR} project (2016). \weblink{http://www.atlantiksolar.ethz.ch/index.html\%3Fp=931.html}{http://www.atlantiksolar.ethz.ch/index.html\%3Fp=931.html}
		\item Contributed performance optimization and control design within the \emph{AtlantikSolar} project, resulting in an 81.5 hour \textbf{endurance world record} perpetual, solar-powered flight for aircraft $<$50kg (2015). \weblink{http://www.atlantiksolar.ethz.ch/index.html\%3Fp=670.html}{http://www.atlantiksolar.ethz.ch/index.html\%3Fp=670.html}
      \end{cvitems}
    } % Description
    {} % website
    {true}
    {}
    
%---------------------------------------------------------
\cvexpentry
  	{Center for Remote Sensing of Ice Sheets (CReSIS), University of Kansas} % Institute
  	{Research Assistant} % Position
    {} % Subject
    {2012 - 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
      	\item Conducted research on control and planning for fixed-wing UAVs including multi-agent avoidance and formation strategies and contributed to the design, integration, and deployment of a UAV outfitted with a dual-frequency ground-penetrating radar.
        \item[] \hspace{-1.2em} \emph{Research / Project Milestones:}
        \item Participated in \textbf{8-week deployment} as mission planner and ground station operator for autonomous operations of a radar-
integrated UAV in \textbf{Western Antarctica}, resulting in \emph{first-ever} bed-rock sounding via a UAV. \weblink{https://cresis.ku.edu/content/research/field-programs/antarctica\#2013}{https://cresis.ku.edu/content/research/field-programs/antarctica\#2013}
      \end{cvitems}
    } % Description
    {} % website
    {true}
    {}
    
\end{cventries}
