%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Summary}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

\descriptionstyle{
%I am an aerial-roboticist with 8+ years research experience on fixed-wing, multirotor, and hybrid vertical-take-off-and-landing (VTOL) unmanned aerial vehicles (UAVs) and a particular passion for (remote) field work. My primary research motivations are geared towards enabling safe, reliable, and useful(!) autonomous vehicle operations in challenging and harsh environments where humans can or should not go.
I am a field roboticist with a specialization on autonomy for flying systems. I have a particular passion for (remote) field work, developing practical algorithms for the purpose of deploying fixed-wing, multirotor, and hybrid vertical-take-off-and-landing (VTOL) unmanned aerial vehicles (UAVs) in challenging conditions or for complex tasks. My primary research motivations are geared towards enabling safe, reliable, and useful(!) autonomous vehicle operations in environments where humans can or should not go.
}\\
\noindent\color{gray}\rule{0.03\textwidth}{0.4pt}\\
%-------------------------------------------------------------------------------
%	CV CONTENT SUMMARY AND NAVIGATION
%-------------------------------------------------------------------------------
\descriptionstyle{
	\hyperref[sec:funding]{\color{awesome}Grants}: Authorship of \textbf{successful} research proposals with funding totaling \textbf{$>$USD 1.7M}. \\
	\hyperref[sec:pub]{\color{awesome}Publications}: As of \today, peer-reviewed publication count: \textbf{31}, h-index: \textbf{12}, citation count: \textbf{548} (source: \headersocialstyle{\ifthenelse{\isundefined{\@gscholar}}{}{\href{https://scholar.google.ch/citations?user=R5Fs1A4AAAAJ\&hl=en}{\faGraduationCap\acvHeaderIconSep Google Scholar}}}).\\
	\hyperref[sec:teaching]{\color{awesome}Mentorship}: \textbf{Supervision} of \textbf{4} Ph.D. students and \textbf{50+} M.Sc. and B.Sc. theses. \textbf{Lecturer} for 2 M.Sc. courses. \textbf{TA} for 2 B.Sc. courses.\\
	\hyperref[sec:field]{\color{awesome}Field experience}: Organization/contributions of/to aerial-robotic field-campaigns in the Arctic, Antarctic, Brazilian Amazon, and Swiss/Italian Alps.
	}%

