%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Teaching}
\label{sec:teaching}
%\vspace{-5mm}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}


%%---------------------------------------------------------
\cvprojwideentry
  	{Lecturer} % Project
  	{Masters Course -- Robot Dynamics (151-0851-00L)} % Project subtext
    {Institute for Robotics and Intelligent Systems, ETH Z\"{u}rich} % Support
    {2015 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item Developed lecture notes, exercises, and presentation material and taught for the fixed-wing portion of the course related to fundamentals of aerodynamics, performance, aircraft design, flight mechanics, and flight control.
		\item Held weekly office hours and bi-weekly exercises.
		\item Designed and graded final examinations.
      \end{cvitems}
    } % Description
    {} % website
    {\showprojectdescriptions}
    {}

%%---------------------------------------------------------
\cvprojwideentry
  	{Student Supervision} % Project
  	{} % Project subtext
    {Autonomous Systems Lab, ETH Z\"{u}rich} % Support
    {2014 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item \textbf{24} Masters Theses
		\item \textbf{18} Masters Semester Projects
		\item \textbf{14} Bachelor Theses
		\item Focus Projects (teams of 8-12 Bachelors Students develop and product from A-Z -- \headersocialstyle{\href{https://asl.ethz.ch/research/focus-projects.html}{\faExternalLink\acvHeaderIconSep https://asl.ethz.ch/research/focus-projects.html}}):
		\begin{itemize}[label=-]
			\item Dipper \headersocialstyle{\href{https://dipper.ethz.ch/index.html}{\faExternalLink\acvHeaderIconSep https://dipper.ethz.ch/index.html}}
			\item ftero (year 1 and 2) \headersocialstyle{\href{https://www.ftero.ch/}{\faExternalLink\acvHeaderIconSep https://www.ftero.ch/}}
			\item VertiGo \headersocialstyle{\href{https://www.vertigoproject.ch/}{\faExternalLink\acvHeaderIconSep https://www.vertigoproject.ch/}}	
		\end{itemize}
      \end{cvitems}
    } % Description
    {} % website
    {\showprojectdescriptions}
    {}
    
%%---------------------------------------------------------
\cvprojwideentry
  	{Guest Lecturer} % Project
  	{Masters Course -- Optimal Controls (KU-AE750)} % Project subtext
    {Department of Aerospace Engineering, University of Kansas} % Support
    {2013} % Date(s)
    {
    	  \begin{cvitems} % Description(s) bullet points
        \item Gave two guest lectures on optimal output feedback control. Topics included derivation of necessary conditions, simulation examples and comparisons with suboptimal methods, and the controller design process using gradient descent numerical methods.
		\item Held a session for KU-AE550 Flight Dynamics class on useful tools in MATLAB for dynamic analysis and simulation.
      \end{cvitems}
    } % Description
    {} % website
    {\showprojectdescriptions}
    {}

%%---------------------------------------------------------
\cvprojwideentry
  	{Undergraduate Teaching Assistant} % Project
  	{Bachelors Courses --} % Project subtext
    {Department of Mathematics, University of Kansas} % Support
    {2010 – 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item Conducted tutor sessions three times a week for class section (apprx. 20-30 students).
		\item Held office hours.
		\item Graded tests, quizzes, and homework.
      \end{cvitems}
    } % Description
    {} % website
    {\showprojectdescriptions}
    {
	  \vspace{-4.0mm}
      \begin{justify}
      \begin{itemize}[leftmargin=2ex, nosep, noitemsep, label={}]
        \setlength{\parskip}{0pt}
     	\item Introduction Topics in Mathematics (KU-MA105)
     	\item Elementary Statistics (KU-MA365)
      \end{itemize}
      \end{justify}
      \vspace{-4.0mm}
    }
\vspace*{-9pt}

\end{cventries}
